Secure Composition \\ of Robust and Optimising Compilers \vspace{-1.5em}

### 2024-05-29 csf2/main.tex
nit

This section introduces trace properties of interest for this paper: \gls*{tms}, \gls*{sms}, \gls*{ms}, \gls*{scct}, and \gls*{ss}.
These properties are of practical importance (as mentioned in \Cref{sec:introduction}) and also of interest in the case study presented later (\Cref{sec:casestud:defs,sec:casestud:rtp}). 
For clarity, this section presents all of them, despite the fact that only property \gls*{scct} is novel, while the other ones are inspired by existing work.
% , none of the properties is novel, for self-containment of the paper, their definition is necessary for the case study.
For each of the presented properties, the technical appendix accompanying the paper defines corresponding monitors, which refine a given property and have a key role in the proofs of this paper.

>>>>

This section introduces trace properties of interest for this paper: \gls*{tms}, \gls*{sms}, \gls*{ms}, \gls*{scct}, and \gls*{ss}.
These properties are of practical importance (as mentioned in \Cref{sec:introduction}) and also of interest in the case study presented later (\Cref{sec:casestud:defs,sec:casestud:rtp}). 
This section presents all of them, despite the fact that only property \gls*{scct} is novel and the others are inspired by existing work, in order to showcase all that is required for a formal proof of security for a realistic compilation toolchain.
% , none of the properties is novel, for self-containment of the paper, their definition is necessary for the case study.
For each of the presented properties, the technical appendix defines corresponding monitors, which refine a given property and have a key role in the proofs of this paper.
